The role of aneuploidy in the evolution of cancer drug resistance

### 2023-06-21 EvolutionaryRescue1.tex
Update EvolutionaryRescue1.tex
added commenting in blue

\usepackage{amssymb,amsmath,amsthm}
\usepackage{commath}
\usepackage[hyphens]{url}
\usepackage[dvipsnames]{xcolor}
\usepackage[unicode=true,colorlinks=true,urlcolor=CadetBlue,citecolor=black,linkcolor=black]{hyperref}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage{authblk}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{lipsum}  
\usepackage[title,page]{appendix}
\usepackage{chngcntr}
%\usepackage{end float}
\usepackage{cleveref}
 \usepackage{subcaption}

%SetFonts
% newtxtext+newtxmath
\usepackage{newtxtext} %loads helv for ss, txtt for tt
\usepackage{amsmath}
\usepackage[bigdelims]{newtxmath}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
%SetFonts

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Density-dependent growth.}

@@

When aneuploid cells are partially resistant to the drug ($\Delta_w\ll0\ll\Delta_a\ll\Delta_m$), evolutionary rescue can be approximated by a one-step evolutionary rescue process where aneuploidy itself rescues the population (\Cref{rescue_prob_wt_growth}). 
When aneuploidy only provides tolerance to the drug ($\Delta_w\ll\Delta_a\ll0\ll\Delta_m$), it cannot rescue the population.
Instead, aneuploidy acts as a \emph{stepping stone} through which the resistant mutant can appear in a more expedient fashion, given that the aneuploid cell population declines slower then the wildtype cell population. In this case, aneuploidy provides two benefits. First, it delays the extinction of the population--providing more time for appearance of the resistance mutations. Second, it increases the population size relative to a wildtype population--providing more cells for generating mutations, i.e., it increases the mutation supply.

>>>>

\usepackage{amssymb,amsmath,amsthm}
\usepackage{commath}
\usepackage[hyphens]{url}
\usepackage[dvipsnames]{xcolor}
\usepackage[unicode=true,colorlinks=true,urlcolor=CadetBlue,citecolor=black,linkcolor=black]{hyperref}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage{authblk}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{lipsum}  
\usepackage[title,page]{appendix}
\usepackage{chngcntr}
%\usepackage{end float}
\usepackage{cleveref}
 \usepackage{subcaption}
\usepackage{xcolor}

%SetFonts
% newtxtext+newtxmath
\usepackage{newtxtext} %loads helv for ss, txtt for tt
\usepackage[bigdelims]{newtxmath}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
%SetFonts

@@

% Daniel commands

\newcommand{\daniel}[1]{\textcolor{blue}{#1}}

@@

\daniel{I think this section has too much of the mathematical derivations, which should instead be in something like Methods. It should focus on just the results.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Density-dependent growth}

@@

When aneuploid cells are partially resistant to the drug ($\Delta_w\ll$(SOMETHING $\ne0$)$\ll\Delta_a\ll\Delta_m$), evolutionary rescue can be approximated by a one-step evolutionary rescue process where aneuploidy itself rescues the population (\Cref{rescue_prob_wt_growth}). 
When aneuploidy only provides tolerance to the drug ($\Delta_w\ll\Delta_a\ll$(SOMETHING $\ne0$)$\ll\Delta_m$), it cannot rescue the population.
Instead, aneuploidy acts as a \emph{stepping stone} through which the resistant mutant can appear in a more expedient fashion, given that the aneuploid cell population declines slower then the wildtype cell population. In this case, aneuploidy provides two benefits. First, it delays the extinction of the population--providing more time for appearance of the resistance mutations. Second, it increases the population size relative to a wildtype population--providing more cells for generating mutations, i.e., it increases the mutation supply.
